Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-07-29 tex/MesnardoBarba2019.tex
Fix typo in URL in footnote

A container is an instance of an image.
The developer builds this image on a local machine and pushes it to a public registry to share it with other users.
Users pull the image from the public registry,---in our case, DockerHub---and create containers out of it.
To create a Docker image, the developer writes a \texttt{Dockerfile}: an ASCII file containing instructions that tell Docker what to do.
For example, we start building a new image from a base image using the keyword \texttt{FROM}.
We then write the different shell instructions (with the \texttt{RUN} instruction) to build a multi-layered runtime environment of the application that includes all its dependencies.
Once we have built and tested the image on the local machine, we push it to a repository on the DockerHub registry: a place to store and retrieve Docker images.
Listing \ref{lst:docker_build_push} provides the command lines to build (\texttt{docker build}) and push (\texttt{docker push}) an image of our CFD software (\texttt{barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu}) that we used to obtain some of the results presented in the next section.
Here, \texttt{CLOUDREPRO} is an environment variable set to the local path of the GitHub repository for this paper, \texttt{cloud-repro},\footnote{\url{https://github.com/barbargroup/cloud-repro}} cloned on the user's machine.

>>>>

A container is an instance of an image.
The developer builds this image on a local machine and pushes it to a public registry to share it with other users.
Users pull the image from the public registry,---in our case, DockerHub---and create containers out of it.
To create a Docker image, the developer writes a \texttt{Dockerfile}: an ASCII file containing instructions that tell Docker what to do.
For example, we start building a new image from a base image using the keyword \texttt{FROM}.
We then write the different shell instructions (with the \texttt{RUN} instruction) to build a multi-layered runtime environment of the application that includes all its dependencies.
Once we have built and tested the image on the local machine, we push it to a repository on the DockerHub registry: a place to store and retrieve Docker images.
Listing \ref{lst:docker_build_push} provides the command lines to build (\texttt{docker build}) and push (\texttt{docker push}) an image of our CFD software (\texttt{barbagroup/petibm:0.4-GPU-IntelMPI-ubuntu}) that we used to obtain some of the results presented in the next section.
Here, \texttt{CLOUDREPRO} is an environment variable set to the local path of the GitHub repository for this paper, \texttt{cloud-repro},\footnote{\url{https://github.com/barbagroup/cloud-repro}} cloned on the user's machine.
